### 2014-09-18 Neutral_simulPow.Rmd
Add functions to test neutral Dq with Anderson-Darling and calculate power

require(pander)
panderOptions('table.split.table',Inf)

This is run only once to generate the metacommunity then set eval=FALSE and generate
a set of parameter files to modify

```{r generateLogSerParms, eval=FALSE,echo=F,message=F,warning=F}
# Generate a SAD for metacommunity using a logseries 
#
# side is the side of the simulation lattice
#
# N is the total number of individuals 
#
# S is the species richness 
#

require(untb)
side <- 500
N <- side*side
S <- 450 
ff<-fisher.ecosystem(N=N,S=S,nmax=N)
plot(ff)
nrow(ff)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
ff$prob <- ff$FreqT/sum(ff$FreqT)

spMeta <- nrow(ff)

# Parameters
#
# Mortality = 0.2 - 0.4
# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
#                         2.5 -> 0.4
# Colonization = 0.001 -0.0001
# Replacement  = 0 - 1

setwd("Simul")
#undebug(genNeutralParms)
# First generate de inp file with species and metacommunity parameters 
genNeutralParms("fishE",500,ff$prob,1,0.2,0.04,0.001)

@@

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,1))

# we need the par file with the simulations parameters

par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100
# Change interval to measure Density and Diversity
par[par$V1=="inter",]$V2 <- 10
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

# Run the model with the parameter ReplacementRate turned on = Hierarchical 
# and exponential dispersal 
#
# Set the location of the binary 
#neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

# copy pomExp.lin to pomac.lin
#system("cp pomExp.lin pomac.lin")

# make simulations
#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

Now I will simulate the model to Time=100 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and ten repetitions

```{r simul_pomac467_T100, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

spMeta <- 467 # nrow(ff) number of species in the generated metacommunity

bName <- paste0("Exp", spMeta) # Base name based in the dispersal "Exp" and number of species in metacommunity "467"

if(simul) {

  # Delete old simulations
  system("rm Exp467T100*")

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 100

  par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0(bName ,"T100") # Time = 100 
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters

  # I have to modify pomExp.lin to make different simulations
  #undebug(genPomacParms)

@@

  system(paste(neuBin,"sim.par","fishE.inp"))
}

m <- compMethods_Time(bName,100,spMeta)

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="SAD",]

# Which are not different
#pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)
# Select a subset to test the procedure !
#
#den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]

require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

# Plot the first pairs not different 
#

mks <- mks1[mks1$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line() + ggtitle("SAD not dif"))

# Plot the first pair different 
#
mks <- mks1[mks1$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line()
 + ggtitle("SAD different"))

# Calculate ranks for each parameter combination with different ReplacementRate
#
den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
den3 <- calcRankSAD(den2)

(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

rm(mks,psa,den2)

#
# Now check differences using multifractals mfSAD o mfSRS
#

# Leer Dq SRS
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))

# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
#

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001, "SRS")
plotDq_ReplaceR(Dq1,0.2,0.4,0.001, "SRS")
plotDq_ReplaceR(Dq1,0.2,0.04,0.001, "SRS")

#mks1 <- m$mPval
#mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
#pander(mks1,split.tables=Inf,caption="SRS not different")

# NO FUNCIONA MERGE
#psa <- mergePairSAD(mks[1,],Dq1)

#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))

plotDq_ReplaceR(Dq1,0.2,0.04,0.001,"DqSAD")
plotDq_ReplaceR(Dq1,0.2,0.4,0.001,"DqSAD")
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001,"DqSAD")

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
#pander(mks1,caption="DqSAD not different")

# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!

compM <- m$compM

mPval <- m$mPval

>>>>

require(pander)
panderOptions('table.split.table',Inf)
options("scipen"=100, "digits"=4)
```

Now I will simulate the model to Time=500 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and ten repetitions

```{r simul_LogSerParms, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

time <- 500
meta <- "L"
side <- 256
nsp  <- 64

if(toupper(meta)=="L") {
  prob <- genFisherSAD(nsp,side)
  neuParm <- "fishE"
  bname <- paste0("neuFish",nsp)
  sadName <- "Neutral"
} else {
  prob <- rep(1/nsp,nsp)  
  neuParm <- "unifE"
  bname <- paste0("neuUnif",nsp)
  sadName <- "NeuUnif"
}

# Parameters
#
# Mortality = 0.2 - 0.4
# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
#                         2.5 -> 0.4
# Colonization = 0.001 -0.0001
# Replacement  = 0 - 1
spMeta <- length(prob)
# First generate de inp file with species and metacommunity parameters 
genNeutralParms(neuParm,side,prob,1,0.2,0.04,0.0001)

# Delete old simulations
system(paste0("rm ",bname,"*.txt"))

# we need the par file with the simulations parameters
par <- read.table("sim.par",quote="",stringsAsFactors=F)

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- time
par[par$V1=="inter",]$V2 <- time # interval to measure Density and Diversity
par[par$V1=="init",]$V2 <- time  # Firs time of measurement = interval
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0(bName ,"T", time ) 
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

@@

genPomacParms("pomExp",1,c(0.2),c(0.04),c(0.0001),c(0,0.001),3)

#genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)

@@

system(paste(neuBin,"sim.par",paste0(neuParm,".inp")))

# Desde aca function compNeutral_Time  
#
fname <- paste0(bname,"T",time,"Density.txt")

den1 <- meltDensityOut_NT(fname,spMeta)

# Test pairwise diferences in SAD
#
mKS <- pairwiseAD_Dif(den1,"value",den1[,1:5])

# Plot the first pairs not different 
#
mks <- mKS[mKS$p.value>0.05,2:ncol(mKS)]
psa <- mergePairSadRank(mks[1,],den1,"value",1:5)
psa <- rbind(psa,mergePairSadRank(mks[nrow(mks),],den1,"value",1:5))
require(ggplot2)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line() + ggtitle("SAD not dif"))

# Build data.frame with proportions
#
#compM <- data.frame(time=Time,notdif=propNotDiffSAD(mKS),method="SAD")

######################### HAY QUE VER DE LOS QUE SON IGUALES si dan distintos con DqSAD /SRS
qNumber <- 35
fname <- paste0(bname,"T",time,"mfOrd.txt")
Dq1 <- readNeutral_calcDq(fname)
Dq1$rep <- rep( 1:(nrow(Dq1)/qNumber),each=qNumber)

mKS1 <- pairwiseAD_Dif(Dq1,"Dq",den1[,c(1:4,10])   #### TEST THIS!

#

### 2014-09-18 SP_simul.Rmd
Add functions to test neutral Dq with Anderson-Darling and calculate power

>>>>

Perform Neutral with metaccomunity uniform and Uniform, 10 simulations with side 256 and 512

```{r test_SAD256U, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

cc <- comp_NeutralUniform(8,256)
DqUN   <-cc$Dq
SadUN  <-cc$SAD

cc <- comp_NeutralUniform(64,256)
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(256,256)
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(8,512)
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(64,512)
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

cc <- comp_NeutralUniform(256,512)
DqUN   <-rbind(DqUN  ,cc$Dq)
SadUN  <-rbind(SadUN ,cc$SAD)

rm(cc)

# merge SAD
SadT <- rbind(SadGC,SadUN)
rm(SadGC,SadUN)

# merge Dq

DqT <- rbind(DqGC,DqUN)
rm(DqGC,DqUN)

setwd(oldcd)
save.image()

#compT <- rbind(compT,compUN)
#SadT <- rbind(SadT,SadUN)
#DqT  <- rbind(DqT,DqUN)

Perform Neutral with metacommunity logseries and Logseries, 10 simulations with side =256/512

```{r test_SAD256, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

cc <- comp_NeutralLogseries(8,256)
DqT   <-rbind(DqT,cc$Dq)
SadT  <-rbind(SadT ,cc$SAD)

cc <- comp_NeutralLogseries(64,256)
DqT   <-rbind(DqT  ,cc$Dq)
SadT  <-rbind(SadT ,cc$SAD)

cc <- comp_NeutralLogseries(256,256)
DqT   <-rbind(DqT  ,cc$Dq)
SadT  <-rbind(SadT ,cc$SAD)

cc <- comp_NeutralLogseries(8,512)
DqT   <-rbind(DqT  ,cc$Dq)
SadT  <-rbind(SadT ,cc$SAD)

cc <- comp_NeutralLogseries(64,512)
DqT   <-rbind(DqT  ,cc$Dq)
SadT  <-rbind(SadT ,cc$SAD)

cc <- comp_NeutralLogseries(256,512)
DqT   <-rbind(DqT  ,cc$Dq)
SadT  <-rbind(SadT ,cc$SAD)

# Simulations with side=512 not done
#
#compSP <- rbind(compSP,compKS_NeutralLogseries(8,512))
#compSP <- rbind(compSP,compKS_NeutralLogseries(64,512))
#compSP <- rbind(compSP,compKS_NeutralLogseries(256,512))
rm(cc)

setwd(oldcd)
save.image()
```

Now check if all simulations are done a make power calculations

```{r power_adtest, eval=T,echo=F,message=F,warning=F}
# Check all simulations are present
require(plyr)
ddply(SadT,3:6,summarize, max(rep))
ddply(DqT,5:8,summarize, max(rep),min(rep))
powad <- data.frame()

powad <- rbind(powad,calcPower_AD(DqT,SadT,8,256))
powad <- rbind(powad,calcPower_AD(DqT,SadT,64,256))
powad <- rbind(powad,calcPower_AD(DqT,SadT,256,256))

powad <- rbind(powad,calcPower_AD(DqT,SadT,8,512))
powad <- rbind(powad,calcPower_AD(DqT,SadT,64,512))
powad <- rbind(powad,calcPower_AD(DqT,SadT,256,512))

save.image()
```

Make plots of power and type I error

```{r power_adtest, eval=T,echo=F,message=F,warning=F}

plot_DqPowerTypeI <- function(pp,tit){
  require(ggplot2)
  pp$Type2[pp$Type2=="SRS"] <- "DqSRS" 
  pp$Type2[grepl("rnz",pp$Type2)] <- "Power"
  pp$Type2[grepl("Dq",pp$Type2)] <- "Type I"

  g <-ggplot(pp, aes(factor(NumSp), power, colour = as.factor(Side))) +
    geom_point(aes(shape=as.factor(Side)),size=4) + ggtitle(tit) + theme_bw() +
    facet_grid(Type1~Type2) + scale_colour_discrete(name="Size") +
    scale_shape_discrete(name="Size") + scale_x_discrete(name="Number of Species")
  print(g)
}
#powad <- power
p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Uniform" ,])
plot_DqPowerTypeI(p1,"Uniform")

p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="NeuUnif" ,])
plot_DqPowerTypeI(p1,"NeuUnif")

p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Logseries" ,])
plot_DqPowerTypeI(p1,"Logseries")

p1 <- with(powad, powad[grepl("^DqSAD|^SRS",Type1) & SAD1==SAD2 & SAD1=="Neutral" ,])
plot_DqPowerTypeI(p1,"Neutral")
